Language-Based Security for Low-Level MPC

### 2024-05-13 ppdp24/examples.tex
checkpoint

@@

\begin{definition}[Conditional Separation]
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
  $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$
  and letting $X = X_1 \cup X_2 \cup X_3$ we have:
  $$\condd{\pmf}{X}{\store'}(\store) =
  \condd{\pmf}{X}{\store'}(\store_{X_2}) *
  \condd{\pmf}{X}{\store'}(\store_{X_3})$$
\end{definition}

\begin{definition}[Conditional Determinism]  
  We write $\conddetx{\pmf}{X_1}{X_2}$ iff for all
  $\store' \in \mems(X_1)$ there exists 
  $\store \in \mems(X_2)$ such that
  $\condd{\pmf}{X_1 \cup X_2}{\store'}(\store) = 1$.
\end{definition}

\begin{lemma}[GMW Invariant]
  \label{lemma-gmwinvariant}
  Given:
  $$ (\varnothing,e) \redxs (\prog,\decodegmw(E[\mesg{z}])) $$
  Then both of the following conditions hold for all $H$ and $C$ where $\iov(\prog) = S \cup M$:
  \begin{enumerate}
    \item $\condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}$
    \item $\conddetx{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}$
  \end{enumerate}
\end{lemma}

\begin{lemma}[And Gate Tactic]
  \label{lemma-gmwtactic}
  %Define:
  %$$
  %\begin{array}{c}
  %  \prog_{i} \defeq \\
  %  \eassign{\mesg{x}}{1}{\flip{x}}{1}; \eassign{\mesg{x}}{2}{\flip{x}}{2}; \\
  %  \eassign{\mesg{y}}{1}{\flip{y}}{1}; \eassign{\mesg{y}}{2}{\flip{y}}{2} 
  %\end{array}
  %$$
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then both of the following conditions hold for both $\cid \in \{ 1,2 \}$ where $\iov(\prog) = M$:
  \begin{enumerate}
   \item $\condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {M_{\{\cid\}} \cup \{ \elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}$
    \item
      $\conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}$
  \end{enumerate}
\end{lemma}

\begin{proof}
Verified automatically using techniques described in Section \ref{section-bruteforce}.  
\end{proof}

>>>>

$$
\OT{\elab{\be_1}{\cid}}{\be_2}{\be_3}
$$
$$
\begin{array}{l}
\solve{\stores}{\OT{\elab{\be_1}{\cid_1}}{\be_2}{\be_3}}{\cid_2} = \\
\qquad ((\solve{\stores}{\be_1}{\cid_1}) \cap 
(\solve{\stores}{\be_2}{\cid_2})) \cup \\
\qquad ((\stores - (\solve{\stores}{\be_1}{\cid_1})) \cap
(\solve{\stores}{\be_3}{\cid_2})
\end{array}
$$

@@

As discussed above and in related work \cite{XXX}, probabilistic
separation conditional on certain variables-- e.g., secret inputs or
public outputs-- is a key mechanism for reasoning about MPC protocol
security. Following \cite{XXX}, we define a conditional separation
relation $\condsep{\pmf}{X_1}{X_2}{X_3}$ to mean that
under the condition of all value assignments for
$X_2$ and $X_3$ are separable under $\pmf$ on the condition
of any value assignment of $X_1$-- i.e., conditionally
on any $\store \in \mems(X_1)$. 
\begin{definition}[Conditional Separation]
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
  $\store' \in \mems(X_1)$ and $\store \in \mems(X_2 \cup X_3)$
  and letting $X = X_1 \cup X_2 \cup X_3$ we have:
  $$\condd{\pmf}{X}{\store'}(\store) =
  \condd{\pmf}{X}{\store'}(\store_{X_2}) *
  \condd{\pmf}{X}{\store'}(\store_{X_3})$$
\end{definition}
Another key concept needed especially for reasoning about
circuits is conditional determinism. For example, if
$\macgv{z}$ is an output of an internal gate, it will
definitely be computed using random variables, however,
it \emph{should} be determistic under any set of input
secrets $S$, since we assume that $\idealf$ is
deterministic.
\begin{definition}[Conditional Determinism]  
  We write $\conddetx{\pmf}{X_1}{X_2}$ iff for all
  $\store' \in \mems(X_1)$ there exists 
  $\store \in \mems(X_2)$ such that
  $\condd{\pmf}{X_1 \cup X_2}{\store'}(\store) = 1$.
\end{definition}

Given these definitions, we can formulate an invariant
for circuit computation with respect to internal gates
as follows. It says that the output of any gate is
deterministic wrt inputs $S$, and conditionally
on $S$ the output $\macgv{\mesg{z}}$ remains
separable from corrupt views and both shares of
$\macgv{\mesg{z}}$. This last nuance is critical,
since those shares will in fact be revealed if
$\macgv{\mesg{z}}$ is decoded as the circuit output. 
\begin{lemma}[GMW Invariant]
  \label{lemma-gmwinvariant}
  Given:
  $$ (\varnothing,e) \redxs (\prog,\decodegmw(E[\mesg{z}])) $$
  Then both of the following conditions hold for all $H$ and $C$ where $\iov(\prog) = S \cup M$:
  \begin{enumerate}
    \item $\condsep{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}{(M_C \cup \{ \elab{\mesg{z}}{1}, \elab{\mesg{z}}{2} \})}$
    \item $\conddetx{\progtt(\prog)}{S}{\{\macgv{\mesg{z}}\}}$
  \end{enumerate}
\end{lemma}
To prove this, we can formulate and automatically prove gate-level
versions of the invariant. This serves as a proof tactic
that simplifies the proof of the GMW invariant.
\begin{lemma}[And Gate Tactic]
  \label{lemma-gmwtactic}
  %Define:
  %$$
  %\begin{array}{c}
  %  \prog_{i} \defeq \\
  %  \eassign{\mesg{x}}{1}{\flip{x}}{1}; \eassign{\mesg{x}}{2}{\flip{x}}{2}; \\
  %  \eassign{\mesg{y}}{1}{\flip{y}}{1}; \eassign{\mesg{y}}{2}{\flip{y}}{2} 
  %\end{array}
  %$$
  Given:
  $$
  \begin{array}{c}
  (\varnothing,\andgmw(z,\mesg{x},\mesg{y}) \redxs %\\
  (\prog,\mesg{z})
  \end{array}
  $$
  Then both of the following conditions hold for both $\cid \in \{ 1,2 \}$ where $\iov(\prog) = M$:
  \begin{enumerate}
   \item $\condsep
      {\progtt(\prog)}
      {\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}
      {\{ \macgv{\mesg{z}} \}}
      {M_{\{\cid\}} \cup \{ \elab{\mesg{z}}{1},\elab{\mesg{z}}{2} \}}$
    \item
      $\conddetx{\progtt(\prog)}{\{ \macgv{\mesg{x}},\macgv{\mesg{y}} \}}{\{ \macgv{\mesg{z}} \}}$
  \end{enumerate}
\end{lemma}
\begin{proof}
Verified automatically using techniques described in Section \ref{section-bruteforce}.  
\end{proof}
